Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
acknowledged neves
some minor todos removed

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:main}. The idea of the
proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
Section ~\ref{sec:background}. Then, we develop various inductive
tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
~\ref{thm:main} in the high genus, genus
one, and genus zero cases respectively. Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.
\todo{Add examples section.}

@@

\begin{defn}
\label{defn:divisor-floor}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\todo{cite lemma 5.4.7 from VZB maybe?}
\end{defn}

@@

Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a). \todo{Ask David, Understand why/whether we need to cite Lemma 5.4.7. we don't just say it at the beginning}

@@

\begin{proof}
Since $X$ has genus 0, general
elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
1$. \todo{Understand why/whether we need to cite 
Lemma 5.4.7.  Peter: What does this mean?}  We see by pole order considerations that

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
We deeply appreciate all of the support that has made our work possible.

>>>>

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:main}. The idea of the
proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
Section ~\ref{sec:background}. Then, we develop various inductive
tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
~\ref{thm:main} in the high genus, genus
one, and genus zero cases respectively. Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.

@@

\begin{defn}
\label{defn:divisor-floor}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\end{defn}

@@

Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a).

@@

\begin{proof}
Since $X$ has genus 0, general
elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
1$. We see by pole order considerations that

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. We thank Jorge Sentieiro Neves help pointing out Reid's bound on the maximal degrees of minimal generators and relations of spin canonical rings.
Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
We deeply appreciate all of the support that has made our work possible.
